Still Missing a Cool Title

### 2006-05-30 talk/dls2006/paper.tex
insert XXX as needed

Despite the constant trend in the programming world towards
portability and reusability, there are some areas in which it is still
notoriously difficult to write flexible, portable, and reasonably
efficient programs.  The implementation of virtual machines is one
such area.  Building implementations of general programming languages,
in particular highly dynamic ones, using a classic direct coding
approach, is typically a long-winded effort and produces a result that
is quite [quite could be removed here?] tailored to a specific
platform and where architectural decisions (e.g. about GC) are spread
across the code in a pervasive and invasive way.

@@

We have implemented other transformations as well, e.g. performing
various optimizations, or turning the whole code into a
continuation-passing style (CPS) [I'm not sure our transformation
can be classified as classical CPS, although there are known similar techniques but the terminology is quite confused] that allows us to use coroutines
without giving up the ability to generate fully ANSI C code.  (This will
be the subject of another paper.)  [mention exception transformer too]

@@

In the example of the \texttt{malloc} operation, replaced by a call to GC
code, this GC code can invoke a complete collection of dead objects, and
can thus be arbitrarily complicated.  Still, our GC code is entirely
written in plain Python, and it manipulates "objects" that are still at
a lower level: pointer and address objects.  Even with the restriction
of having to use pointer-like and address-like objects, Python remains
more expressive than, say, C to write a GC.  [see also Jikes]

>>>>

Despite the constant trend in the programming world towards
portability and reusability, there are some areas in which it is still
notoriously difficult to write flexible, portable, and reasonably
efficient programs.  The implementation of virtual machines is one
such area.  Building implementations of general programming languages,
in particular highly dynamic ones, using a classic direct coding
approach, is typically a long-winded effort and produces a result that
is quite [XXX quite could be removed here?] tailored to a specific
platform and where architectural decisions (e.g. about GC) are spread
across the code in a pervasive and invasive way.

@@

We have implemented other transformations as well, e.g. performing
various optimizations, or turning the whole code into a
continuation-passing style (CPS) [XXX I'm not sure our transformation
can be classified as classical CPS, although there are known similar techniques but the terminology is quite confused] that allows us to use coroutines
without giving up the ability to generate fully ANSI C code.  (This will
be the subject of another paper.)  [XXX mention exception transformer too]

@@

In the example of the \texttt{malloc} operation, replaced by a call to GC
code, this GC code can invoke a complete collection of dead objects, and
can thus be arbitrarily complicated.  Still, our GC code is entirely
written in plain Python, and it manipulates "objects" that are still at
a lower level: pointer and address objects.  Even with the restriction
of having to use pointer-like and address-like objects, Python remains
more expressive than, say, C to write a GC.  [XXX see also Jikes]
